The Spine of American Legal Practice

### 2016-06-29 article/article.Rmd
Make text of the sections part of the article

Having divided the texts according to a historically justified pattern, our next step was to compare each section to every other section and measure the similarity between them. To continue the New York-to-California example, consider the following pairs of sections. The first pair is from the final draft of the New York Field Code. These sections completely abolished prior practice and began to rebuild the procedure system from the ground up:

> § 554. The distinction between actions at law and suits in equity, and the forms of all such actions and suits, heretofore existing, are abolished; and, there shall be in this state, hereafter, but one form of civil action, for the enforcement or protection of private rights and the redress or prevention of private wrongs, which shall be denominated a civil action. § 555. In such action, the party complaining is known as the plaintiff, and the adverse party as the defendant.

In the theory of Euro-American lawyers, California had no prior practice to abolish, so the code began more simply:

> § 1. There shall be in this State but one form of Civil Action, for the enforcement or protection of private rights, and the redress or prevention of private wrongs. §2. In such action the party complaining shall be known as the plaintiff, and the adverse party as the defendant.

@@

```{r code-to-code-network, fig.width=6.5, fig.height=7, fig.cap = "The structure of borrowings among nineteenth-century codes of civil procedure. Note that several versions of New York's Field Code were at the center of the network, while other states such as California and Ohio became centers of regional variations on the Field Code. States that adopted any of the variations on the Field Code became part of a network centered on New York capital."} 
set.seed(3728)
ggraph(codes_g, "igraph", algorithm = "nicely") +
  geom_edge_fan(aes(edge_width = sections_borrowed, 
                    alpha = sections_borrowed),
                arrow = arrow(type = "closed", ends = "first",
                              length = unit(0.20, "inches"),
                               angle = 15)) + 
  geom_node_point(aes(shape = as.factor(distance)), size = 5) +   
  scale_edge_width("Sections borrowed", range = c(1, 2), guide = "none") +    
  scale_edge_alpha(range = c(0.3, 0.6), guide = "none") +   
  scale_color_discrete("Distance from a Field Code") +
  ggforce::theme_no_axes() +  
  geom_node_text(aes(label = name), size = 3, family = "Palatino") +
  labs(title = "The migration of the Field Code",
       subtitle = "Codes of civil procedure connected by borrowed sections") +
  theme(legend.position = "bottom",
        panel.border = element_blank(),
        text = element_text(family = "Palatino"),
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 8),
        plot.title = element_text(face = "bold"))
```

>>>>

Having divided the texts according to a historically justified pattern, our next step was to compare each section to every other section and measure the similarity between them. To continue the New York-to-California example, consider the following pairs of sections. The first pair is from the final draft of the New York Field Code. These sections completely abolished prior practice and began to rebuild the procedure system from the ground up (figure 3).

![Final Report of the Commissioners on Practice and Pleadings (New York, 1850), 225--25,  §§ 554--555.](NY1850-text.png)

In the theory of Euro-American lawyers, California had no prior practice to abolish, so the code began more simply (figure 4).

![1851 California Laws 51 §§ 1--2.](CA1851-text.png)

@@

```{r code-to-code-network, fig.width=6.5, fig.height=7, fig.cap = "The structure of borrowings among nineteenth-century codes of civil procedure. Note that several versions of New York's Field Code were at the center of the network, while other states such as California and Ohio became centers of regional variations on the Field Code. States that adopted any of the variations on the Field Code became part of a network centered on New York capital."} 
set.seed(3728)
ggraph(codes_g, "igraph", algorithm = "nicely") +
  geom_edge_fan(aes(edge_width = sections_borrowed, 
                    alpha = sections_borrowed),
                arrow = arrow(type = "closed", ends = "first",
                              length = unit(0.20, "inches"),
                               angle = 15)) + 
  geom_node_point(aes(color = as.factor(distance)), size = 5) +   
  scale_edge_width("Sections borrowed", range = c(1, 2), guide = "none") +    
  scale_edge_alpha(range = c(0.3, 0.6), guide = "none") +   
  scale_color_discrete("Distance from a Field Code") +
  ggforce::theme_no_axes() +  
  geom_node_text(aes(label = name), size = 3, family = "Palatino") +
  labs(title = "The migration of the Field Code",
       subtitle = "Codes of civil procedure connected by borrowed sections") +
  theme(legend.position = "bottom",
        panel.border = element_blank(),
        text = element_text(family = "Palatino"),
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 8),
        plot.title = element_text(face = "bold"))
```
